Title

### 2024-10-10 Theory recap/notes.tex
test

Then the equilibrium point $\left( x_{*}, u_{*}, \nu_{*}, \omega_{*} \right)$ is computed,

>>>>

Then the equilibrium point $\left( x_{*}, u_{*}, \nu_{*}, \omega_{*} \right)$ is computed.

\subsection*{ETM definition}
Different approaches were used in \cite{css-paper} and \cite{css-extended}, the first work takes into account the difference between the input and output vectors of the network at different time instants, the latter instead directly uses the sector conditions as the triggering ones.
